On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-14 manuscripts/PNAS/chazthm_pnas.tex
fixed pnas weirdness
last edit
clarify thm 2

\begin{theorem}\label{robustPolythm}
There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}). In particular, either no substitutions impart to $Y$ this property or all but a Borel set of measure zero do.
\end{theorem}

@@

Thus, choosing the dictionary and sparse codes ``randomly'' from \emph{any} continuous distribution generates data with stable sparse representations almost certainly.

@@

\clearpage

@@

>>>>

\begin{theorem}\label{robustPolythm}
There is a polynomial $g$ in the entries of $\mathbf{A}$ and $\mathbf{x}_i$ with the following property:  if $g$ evaluates to a nonzero number and more than \mbox{$(k-1){m \choose k}$} of the resulting $\mathbf{x}_i$ are supported on each $S \in E$ for some regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ (Def.~\ref{maindef}). In particular, all -- except for a Borel set of measure zero -- substitutions impart to $Y$ this property.
\end{theorem}

@@

Thus, choosing the dictionary and sparse codes ``randomly'' almost certainly generates data with stable sparse representations.

@@

\pnasbreak

@@

\pnasbreak
